Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
fix bastille 2018

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while re-sampling at 500 m , 750 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017). Multilayer networks consisted of the social
associations between `r DT[, uniqueN(get(idcol))]` individuals across three
habitat layers (foraging, forest and open) for the entire study period. For each
land cover resolution, we calculated individual graph strength within each
habitat layer, and edge overlap and multidegree across habitat layers.

>>>>

### Spatial scale
To assess the influence of spatial scale, we aggregated the land cover raster
using the R package `grainchanger` [@Graham_2019] across a series of scales (100
- 1000 m by steps of 100 m). The land cover raster was aggregated using a modal
moving window method using a circular window corresponding to the above scales
[@Graham_2019a]. We assume 30 m and 100 m represents fine-scale decision making
for caribou during foraging, while 500 - 1000 m represents the scale at which
caribou tend to select and avoid habitat [@Bastille_2018].
Multilayer networks consisted of the social associations between 
`r DT[, uniqueN(get(idcol))]` individuals across three habitat layers (foraging, 
forest and open) for the entire study period. For each land cover resolution, we
calculated individual graph strength within each habitat layer, and edge overlap
and multidegree across habitat layers.
